Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2015-10-22 Report/convergence_centralized.tex
reverted most of the changes

Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear. Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both. The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively. Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
	\begin{equation}
		\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
	\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

The following conditions are required to prove the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative approach.
\begin{itemize}
	\item[(a)] Objective function should be bounded below
	\item[(b)] Feasible set should be a compact
	\item[(c)] Sequence of objective values should be strictly decreasing
	\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}. However, to ensure strict monotonicity of the objective sequence, we need condition (d). Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of objective sequence can be shown by using \cite[Th. 3.14]{rudin1964principles}. Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we can show that \reviewF{every limit point of the sequence of iterates is a stationary point of the nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates correspond to the stacked vector of solution obtained in each iteration.

Before proceeding further, we denote the representations used in the following proof. Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} correspond to the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1}, such as \me{\beta_{l,k,n},\gamma_{l,k,n}} or \eqn{t_{l,k,n},\epsilon_{l,k,n}} respectively. Let \me{\iter{\mx}{k}{i}} and \me{\iter{\mz}{k}{i}} be the solution obtained in \eqn{\ith{i}} \ac{AO} step of \eqn{\ith{k}} \ac{SCA} iteration for the optimization variables \me{\mx} and \me{\gamma} with fixed \me{\my}. Let \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{|\my}{i}} be the solution obtained for \me{\mx} and \me{\mz} when \ac{SCA} iteration converges as \eqn{k \rightarrow \infty} in the \eqn{\ith{i}} \ac{AO} step for fixed \eqn{\my}. Similarly, \me{\iter{\my}{\lpointx}{i}} and \me{\iter{\mz}{|\mx}{i}} correspond to the solutions of \eqn{\my} and \eqn{\mz} in \eqn{\ith{i}} \ac{AO} update for fixed \eqn{\mx}, \textit{i.e.}, upon convergence of the \ac{SCA} loop as \eqn{k \rightarrow \infty}.

@@

\review{To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{x}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{x}) &=& \hat{f}(\mbf{x}) + {\tau}_k^{(i)} \, \| \mbf{x} - \mbf{x}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{x}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{x}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}. Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}}.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
\review{In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.}

@@

Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}. Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}. Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for the variable \me{\mx} and \me{\mz} is given by

@@

The feasible set defined by the problem in \eqref{con-m} is denoted as \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}. To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields 

@@

\review{However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows

@@

since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of the objective sequence in each \ac{AO} step \eqn{{i}}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon the convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

\review{Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured. It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.}

@@

In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm. In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}. Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}. The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.

%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.  Note that similar claim cannot be made for the convergence of \eqn{\{\ma^t\}}, since the sequence is not monotonic. However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}. By considering two different convergent subsequences of \eqn{\{\ma^t\}}, say, \eqn{\{\ma^{t_i} \, | \, i = 0,1,\dotsc\}} and \eqn{\{\ma^{t_k} \, | \, k = 0,1,\dotsc\}} that converges to two different limit points, such that
\begin{equation}
\lim_{t \rightarrow \infty} {f}(\ma^t) = \lim_{i \rightarrow \infty} {f}(\ma^{t_i}) = \lim_{k \rightarrow \infty} {f}(\ma^{t_k})
\end{equation}
we can show that \eqn{\{\ma^t\}} is not a convergent sequence.

Since \eqn{\{\ma^t\}} is not a convergent sequence, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
\end{equation}
Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation}
\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma})
\end{equation}
moreover, note that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0} and
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
\end{equation}
where \eqn{\mc{Q}} is the feasible set defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}. Eq. \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}. Hence, the limit point of any convergent subsequence \eqn{\bar{\ma}} is a stationary point of \eqref{con-m}.

@@

To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}, and is regular as it satisfies the Slater's constraint qualifications. Therefore, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
	\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as
\begin{equation} \label{rhs_equiv}
	\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. By using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the iterative algorithm is a stationary point of \eqref{con}.}

>>>>

The following conditions are required to show the convergence of Algorithm \ref{algo-1}, which is used to solve problems \eqref{eqn-6} and \eqref{eqn-mse-1} in an iterative manner.
\begin{itemize}
	\item[(a)] Objective function should be bounded below
	\item[(b)] Feasible set should be compact
	\item[(c)] Sequence of objective values should be strictly decreasing
	\item[(d)] Uniqueness of the minimizer in each step.
\end{itemize}
\review{The conditions (a), (b), and (c) are required to prove the convergence of objective sequence generated by Algorithm \ref{algo-1}. However, to ensure strict monotonicity of the objective sequence, we require condition (d). Therefore, by assuming (a), (b), and (c) are satisfied by Algorithm \ref{algo-1}, the convergence of the objective sequence can be shown by using \cite[Th. 3.14]{rudin1964principles}. Finally, by using the discussions in \cite{marks1978technical,lanckriet2009convergence,scutari_1}, we show that \reviewF{every limit point of the sequence of iterates generated by Algorithm \ref{algo-1} is a stationary point of nonconvex problems \eqref{eqn-6} and \eqref{eqn-mse-1}}. The term iterates denotes the stacked vector of solution variables obtained in each iteration.}

Before discussing the convergence analysis, let us consider a generalized formulation for the problems in \eqref{eqn-6} and \eqref{eqn-mse-1} as
\begin{IEEEeqnarray}{RcL} \label{con} \neqsub
	\underset{\mx,\my,\mz}{\text{minimize}} &\quad& \hat{f}(\mx,\my,\mz) \eqsub \label{con-obj} \\
	\text{subject to} &\quad& h(\mz) - g_0(\mx,\my) \leq 0 \eqsub \label{con-dc} \\
	&\quad& g_1(\mx,\my) \leq 0 \eqsub \label{con-cvx-blk} \\
	&\quad& g_2(\mx) \leq 0 \eqsub \label{con-cvx}
\end{IEEEeqnarray}
where the functions \me{g_2} and \me{\hat{f}} are convex, and the function \me{h} is linear. Let functions \me{g_0} and \me{g_1} be convex w.r.t either \me{\mx} or \me{\my}, but not jointly convex on both variables. The constraint \eqref{con-dc} corresponds to \eqref{eqn-6.2} or \eqref{eqn-mse-1.2} and the constraint \eqref{con-cvx-blk} corresponds to \eqref{eqn-6.3} or \eqref{eqn-mse-1.3} respectively. Other convex constraints are handled by \eqref{con-cvx} and the feasible set of \eqref{con} is given by 
\iftoggle{single_column}{
	\begin{equation}
		\mc{F} = \{ \; \mx,\my,\mz \; \big | h(\mz) - g_0(\mx,\my) \leq 0, g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
	\end{equation}
}{\begin{align}
\mc{F} = \{ \; \mx,\my,\mz \; \big | & \quad h(\mz) - g_0(\mx,\my) \leq 0, \nonumber \\
& \quad g_1(\mx,\my) \leq 0, g_2(\mx) \leq 0 \}.
\end{align}}

\review{We use the following notations to discuss the convergence proof. Since Algorithm \ref{algo-1} involves two nested iterations, \textit{i.e.}, one for \ac{SCA} and another one for \ac{AO}, we denote \ac{AO} step by a superscript \me{(i)} and \ac{SCA} iteration by a subscript \me{k}. Let \me{\mx}, \me{\my}, and \me{\mz} be the stacked vector all transmit precoders, receive beamformers, and other optimization variables present in the formulations \eqref{eqn-6} and \eqref{eqn-mse-1} respectively. Since Algorithm \ref{algo-1} includes two \ac{SCA} iterations performed until convergence in each \ac{AO} iteration, let us now consider \ac{AO} step \eqn{i} for fixed \eqn{\my}. The solution obtained at the \eqn{\ith{k}} \ac{SCA} step is represented as \eqn{\mx=\iter{\mx}{k}{i}} and \eqn{\mz=\iter{\mz}{k}{i}}. As \eqn{k \rightarrow \infty}, the objective sequence converges, and the corresponding solution obtained is denoted as \me{\iter{\mx}{\lpointx}{i}} and \me{\iter{\mz}{\lpointx|\my}{i}}. Similarly, for fixed \eqn{\mx} and as \eqn{k \rightarrow \infty}, the corresponding solution obtained is represented as \me{\my = \iter{\my}{\lpointx}{i}} and \me{\mz = \iter{\mz}{\lpointx|\mx}{i}} respectively.}

@@

To ensure the uniqueness of the transmit and the receive beamformers, the objective function of the convex subproblems in \eqref{eqn-9} and \eqref{eqn-mse-2} are regularized by a strongly convex function in each \ac{SCA} iteration \eqn{k} and \ac{AO} update step \eqn{i} as 
\begin{IEEEeqnarray}{rCl} \neqsub
	\hat{f}(\mbf{z}) &=& \| \tilde{\mbf{v}} \|_q \eqsub \label{orig_obj} \\ 
	f(\mbf{z}) &=& \hat{f}(\mbf{z}) + {\tau}_k^{(i)} \, \| \mbf{z} - \mbf{z}^{(i)}_{k} \|^2_2 \eqsub \label{mod_obj} 
\end{IEEEeqnarray}
where \eqn{\mbf{z}} is a vector stacking all optimization variables, which can be either \eqn{[\mx,\iter{\my}{\lpoint}{i-1},\mz]} or \eqn{[\iter{\mx}{\lpoint}{i},\my,\mz]} depending on the problem and \eqn{\mbf{z}^{(i)}_{k} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} is the solution obtained in the previous \eqn{\ith{(k-1)}} \ac{SCA} step. The positive constant \me{{\tau}_{k}^{(i)} > 0} ensures the strong convexity of \eqn{f} in each step and \eqn{c > 0} be the constant of strong convexity, defined as \eqn{c \triangleq \min_{k} \{{\tau}_{k}^{(i)}\}}, as shown in \cite{scutari-1}. Thus, due to the strong convexity of \eqn{f} in \eqref{mod_obj}, uniqueness of the minimizer is guaranteed in each \ac{SCA} step as discussed in \cite{yang_yang,scutari-1}.

@@

\subsection{Strict Monotonicity of the Objective Sequence} \label{mcity}
In the following discussions, we consider the modified objective \eqn{f} in \eqref{mod_obj} instead of \eqn{\hat{f}} due to the uniqueness of the minimizer and upon convergence of the objective, \eqn{f} is equal to \eqn{\hat{f}}. Therefore, the discussions are valid for the \ac{JSFRA} problem in \eqref{eqn-6} by regularizing the objective \eqref{eqn-6.1} as \eqref{mod_obj}.

@@

Let \me{\iter{\mc{X}}{k}{i}} be the feasible set for the \eqn{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for a fixed \me{\iter{\my}{\lpoint}{i-1}} and \me{\iter{\mx}{k}{i}}. Similarly, \me{\iter{\mc{Y}}{k}{i}} denotes the feasible set for a fixed \me{\iter{\mx}{\lpoint}{i}} and \me{\iter{\my}{k}{i}}. Using \eqref{con-relax}, the convex subproblem for the \me{\ith{i}} \ac{AO} iteration and the \me{\ith{k}} \ac{SCA} point for variables \me{\mx} and \me{\mz} is given by

@@

The feasible set defined by the problem \eqref{con-m} is denoted by \me{\iter{\mc{X}}{k}{i} \subset \mc{F}}. To prove the convergence of the \ac{SCA} updates in the \me{\ith{i}} \ac{AO} iteration, let us consider that \eqref{con-m} yields 

@@

However, to ensure strict monotonicity of the objective sequence, we rely on the modified objective in \eqref{con-obj-m}, which is strongly convex with some parameter \eqn{c > 0}. Now, to show strict monotonicity, let us consider \eqn{\mbf{z}_{k}^{(i)} \triangleq [\mx_{k}^{(i)},\iter{\my}{\lpoint}{i-1},\mz_{k}^{(i)}]} as the minimizer for \eqref{con-m} in the \eqn{\ith{(k-1)}} \ac{SCA} step and let \eqn{\iter{\mbf{z}}{k+1}{i}} be the minimizer in the \eqn{\ith{k}} step. At the \eqn{\ith{k}} \ac{SCA} iteration, \eqn{\forall \mbf{z} \in \mc{X}_{k}^{(i)}}, it follows

@@

since \eqn{\iter{\mbf{z}}{k+1}{i}} is the solution. Using \eqref{strict_monotonicity} and \eqn{\iter{\mbf{z}}{k}{i} \in \iter{\mc{X}}{k}{i}}, we can show that \eqn{f(\iter{\mbf{z}}{k}{i}) > f(\iter{\mbf{z}}{k+1}{i})} holds in each \ac{SCA} step unless \eqn{\mbf{z}_{k}^{(i)} \rightarrow \mbf{z}_{\lpoint}^{(i)}} as \eqn{k \rightarrow \infty}. Now using the facts that (i) \eqn{\{f(\mbf{z}^{(i)}_k)\}} is monotonic, and (ii) the uniqueness of the minimizer (see \eqref{strict_monotonicity}), strict monotonicity of \eqn{\{f(\mbf{z}^{(i)}_k)\}} is ensured \cite{scutari2010convex}. Now, by using the fact that the objective sequence is strictly nonincreasing and bounded, we can ensure the convergence of objective sequence in each \ac{AO} step \eqn{{i}} and \reviewF{\eqn{\mbf{z}_{\lpoint}^{(i)} \triangleq \{\iter{\mx}{\lpoint}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{\lpoint|\my}{i}\}} is the solution obtained upon convergence of the objective sequence \eqn{\{f(\mbf{z}_k^{(i)})\}} in the \eqn{\ith{i}} \ac{AO} iteration.}

@@

Using \eqref{strict_monotonicity}, strict monotonicity of the objective \eqref{mod_obj} while alternating the optimization variables from \eqn{\mx,\mz} to \eqn{\my,\mz} in the \eqn{\ith{i}} \ac{AO} update can also be ensured. It follows from that fact that \eqn{\iter{\mbf{z}}{\lpoint}{i}} is included in the feasible set \eqn{\mc{Y}_{0}^{i}}, and therefore the objective function follows \eqref{fixed_point} strictly in each \ac{AO} update.

@@

In this section, we discuss the convergence of the sequence of iterates generated by the iterative algorithm. In order to do so, let us use single global index \eqn{t} to represent both \ac{SCA} indexing \eqn{k} and \ac{AO} index \eqn{i}. Using this, we can represent \eqn{\ma^{t} \triangleq [\iter{\mx}{k}{i},\iter{\my}{\lpoint}{i-1},\iter{\mz}{k|\my}{i}]} as a stacked vector of solution obtained in the \eqn{\ith{k}} \ac{SCA} step of the \eqn{\ith{i}} \ac{AO} update with fixed \eqn{\my}. The index \eqn{t} is used to represent both \ac{SCA} updates involving transmit and receive beamformers within each \ac{AO} step.

%Additionally, we can also ensure the convergence of \eqn{\{\hat{f}(\ma^t)\}}, since the regularization term in \eqref{mod_obj} vanishes as \eqn{t \rightarrow \infty}, \eqn{\|\ma - \ma^t\|^2 \rightarrow 0}.
Using the discussions in Appendices \ref{b_obj} and \ref{mcity}, we can show that the sequence of objective values \eqn{\{f(\ma^t)\}} converges.  Note that similar claim cannot be made on the convergence of \eqn{\{\ma^t\}}, since the sequence need not be monotonic. However, due to the compactness of the feasible set, the sequence of iterates \eqn{\{\ma^t\}} is bounded. Therefore, there exists at least one subsequence that converges to a limit point in the feasible set \cite[Th. 3.6]{rudin1964principles}. Since there can be possibly two subsequences of \eqn{\{\ma^t\}} that converges to two different limit points, the sequence of iterates \eqn{\{\ma^t\}} need not be convergent sequence.

Therefore, we can only claim that every limit point of the sequence \eqn{\{\ma^t\}} is a stationary point, \textit{i.e.,} the limit point of every convergent subsequence is a stationary point. To prove that, let us consider a subsequence \eqn{\{\ma^{t_j} \, | \, j = 0,1,\dotsc\}} of \eqn{\{\ma^t\}} that converges to a limit point \eqn{\bar{\ma}}, where \eqn{\bar{\ma} = \lim_{j \rightarrow \infty} \ma^{t_j}}. It follows from \eqref{con-convergence}, \eqref{strict_monotonicity}, and \eqref{fixed_point} that
\begin{equation} \label{seq_mon}
f(\ma^{t_{j+1}}) < f(\ma^{t_{j}}) < f(\ma^{t_{j-1}}).
\end{equation}
Eq. \eqref{seq_mon} holds strictly while alternating the optimization variables as shown in \eqref{fixed_point}. Now, by taking the limit as \eqn{j \rightarrow \infty} and by using the continuity of objective function \eqn{f}, we obtain
\begin{equation} \label{limpoint}
\lim_{j \rightarrow \infty} f(\ma^{t_j}) = f(\lim_{j \rightarrow \infty} \ma^{t_{j}}) = f(\bar{\ma}).
\end{equation}
Using strict monotonicity in \eqn{\{f(\ma^{t_j})\}} and the fact that as \eqn{j \rightarrow \infty}, \eqn{|f(\ma^{t_{j}}) - f(\ma^{t_{j+1}})| \rightarrow 0}, we can show that limit point \eqn{\bar{\ma}} satisfies the optimality condition \cite[Prop. 2.1.2]{bertsekas1999nonlinear} as 
\begin{equation} \label{seq_mon1}
\nabla f (\bar{\ma}) (\ma - \bar{\ma}) \geq 0, \; \fall \ma \in \mc{Q} \subset \mc{F} \eqsub
\end{equation}
where \eqn{\mc{Q}} is a convex subset defined by \eqref{con-dc-m} and \eqref{con-cvx-blk-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}. Hence, the limit point \eqn{\bar{\ma}} is a stationary point of \eqref{con-m} as \eqn{k \rightarrow \infty, i \rightarrow \infty}.

@@

To prove the feasibility of the limit point \me{\bar{\ma}}, note that in each \ac{SCA} step, the feasible sets \eqn{\mc{X}_{k}^{(i)},\mc{Y}_{k}^{(i)} \subset \mc{F}}. Therefore, the limit point \eqn{\bar{\ma} \in \mc{F}}. Since \eqn{\bar{\ma}} satisfies Slater's constraint qualifications, there exist Lagrange multipliers \eqn{\mu_i} such that
\begin{equation} \label{kkt_mod_expr}
	\textstyle \nabla f(\bar{\ma}) + \mu_0 \big [ \nabla h(\bar{\ma}) - \nabla\hat{g}_0(\bar{\ma};\bar{\ma}) \big ] + \sum_{i=1}^2 \mu_i \nabla g_i(\bar{\ma}) = 0.
\end{equation}
The relation between \eqref{kkt_expr} and \eqref{kkt_mod_expr} is evident by the following facts: (i) The quadratic term \eqn{\|\ma - \ma^{t_j}\|^2} in \eqref{mod_obj} vanishes as \eqn{j \rightarrow \infty, \ma^{t_j} \rightarrow \bar{\ma}}, since we assume that \eqn{\bar{\ma}} is the limit point of convergent subsequence \eqn{\{\ma^{t_j}\}}. Therefore, the gradient evaluated at \eqn{\bar{\ma}} satisfies \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})}. (ii) Additionally, by using the relation in \eqref{con-relax}, the gradient of the constraint \eqref{con-dc} evaluated at \eqn{\bar{\ma}} is given as
\begin{equation} \label{rhs_equiv}
	\nabla h(\bar{\ma}) - \nabla \hat{g}_o(\bar{\ma};\bar{\ma}) = \nabla h(\bar{\ma}) - \nabla g_o(\bar{\ma}).
\end{equation}
Now, by applying the relation \eqref{rhs_equiv} and \eqn{\nabla {f}(\bar{\ma}) = \nabla \hat{f}(\bar{\ma})} in \eqref{kkt_mod_expr}, we can show that the limit point \eqn{\bar{\ma}} satisfies \eqref{kkt_expr}. By using \cite[Thms. 2 and 11]{scutari_1} and \cite[Prop. 3.2]{amir}, we can show that every limit point of the sequence of iterates \eqn{\{\ma^t\}} generated by the algorithm is a stationary point of problem \eqref{con}.}
